Where Do Population III Stars Form?

### 2019-05-07 paper.tex
Added P3 spread in creation time plot, as well it's description within the results. Adjusted a few other things here and there.

Once a halo becomes chemically enriched by the death of its Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10, Smith15}. Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars. These stars still are metal-poor, having metallicities of 10$^{-6}$ - 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to PopIII stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2000 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and uses the cosmological parameters from the Planck collaboration best fit 
\citet{Planck13_Cosmo}: $\Omega_{M}$ = 0.3175, $\Omega_{\Lambda}$ = 
0.6825, $\Omega_{DM}$ = 0.2685, and h = 0.6711, with the variables 
having their usual definitions. The simulation is run until $z$ = 9.32, when it becomes too computationally expensive to continue. At this point, 20\% of the volume is ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.

@@

If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from W12 \citep{Hirano17}. This results in an exponential cutoff before M$_{\rm char}$ and a power-law IMF after. Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}, we are only tracking massive Pop III star formation.

@@

%====================================================================
\subsubsection{Pop II  Star Formation and Feedback}
%====================================================================
The Pop II star formation model is the same as \citet{Wise09}, which is equivalent to the above criteria for Pop III star formation but without the molecular hydrogen fraction requirement, and with a metallicity greater than the above value. Star formation is only allowed for gas with temperatures $T$ < 1000 K, to ensure that the volume is cold and collapsing. Contrary to Pop III stars representing single star particles, metal-enriched star particles are modelled as clusters of stars. We enforce a minimum mass of M$_{min}$ = 1000 M$_{\odot}$ for these star particles.

@@

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor can affect the column density of \hh{}, we can examine $N_{\rm H2}$ to the core as a function of halo mass for an isothermal halo, with a constant \hh{} fraction. The total number of \hh{} molecules within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c}$ is the critical density. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}
Here, $f_{c} = 10^{-2}$ and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$. For $z = 15$ and $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, Figure \ref{fig:H2_column_mass} shows the \hh{} column density as a function of halo mass. As the shielding factor is increases, the column density can effectively increase by an order of magnitude. The effect of the shielding factor on the column density of \hh{} within a halo is critical in understanding how LW feedback might affect these halos.

@@

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$50 particles.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
    \caption{The star formation rate density of Pop III stars. It peaks at a redshift of 20, and slowly falls off. Note that metal-enriched star formation continually increases throughout time, although that is not plotted here.}
    \label{fig:pop3_SFR_bar}
\end{figure}

In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}. The median for each bin is by an x, and the 15.9\% and 84.1\% are plotted below and above the mean, respectively. The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq. \ref{LWbg} is shown as the black solid line. Notably, the mean halo mass falls well below the relation, at 10$^{5.9}$ M$_{\odot}$ until $z$ = 11.5, at which point, the mean halo mass rises to 10$^{6.6}$ M$_{\odot}$. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times. In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts. Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}. As can be seen by the red solid line in \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation. The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times. This galaxy has a halo mass of $10^{8.5} M_{\odot}$, a total stellar mass of $10^{6.5} M_{\odot}$, and has a peak Pop III SFR of $10^{-3.5} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $10^{-1.3}$ at $\approx$ 500 Myr. This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars. This increase in the LW background can also be seen in Figure \ref{fig:JLW_xe_mass}, where by the end of the simulation, the LW background rises to greater than 1 $J_{21}$.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus redshift. The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass. The error bars indicate the 15.9\% and 84.1\% percentiles. Plotted along the right hand side is the percentage of halos that fall below the M01 mass threshold, also plotted along redshift. The M01 mass threshold (Eq. \ref{mthresh}), is plotted for the constant LW background in Eq. \ref{LWbg}. Almost all halos fall below the M01 relation, until $z$ = 11.5, when the mean halo mass rises above the relation.}
    \label{fig:mean_mass}
\end{figure}

@@

The LW background intensity versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}. Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq. \ref{mthresh}) for the given LW background (Eq. \ref{LWbg}) is the solid black line. We see again that almost all halos form Pop III stars below the M01 threshold. There are also a few halos that form Pop III stars in very high J$_{\rm LW}$, below the relation. This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 100 pc of each other. Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation. The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs synchronically, star formation will not be suppressed, so long as they are a suitable distance away from each other. As there are only a few data points in this region, this situation is rare. It should be noted that there are duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation. The grouped points in the higher end of J$_{\rm LW}$ are representative of such halos. We find that a total of 84\% of the halos forming Pop III stars lie below the M01 mass threshold over the entire simulation redshift range. We also do not see a clear relationship between the LW intensity and the host halo mass. This may be showing that the LW intensity is not as great an indicator of which halo will be allowed to for a Pop III star as previously thought.

@@

We now inspect the number of Pop III stars and the total mass of Pop III stars per halo. Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses < $1 M_{\odot}$. Figure \ref{fig:totnump3_halomass_sidehist} shows the number of Pop III stars per halo for a given halo mass, just after star formation. The histogram of the number of Pop III stars for all masses is projected on the right hand side. We find that a median number of four Pop III stars form per halo, with a maximum of 16 Pop III stars forming per halo. Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo. Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars. It should be noted that these halos aren't necessarily forming all of the Pop III stars at once. For example, a halo can form stars again if it din't host a supernova. The number of Pop III stars that form within a halo is indicative of the star formation history of that halo. At the end of the simulation, Figure \ref{fig:final_redshift_Np3_mass} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star. The red line shows the median number of Pop III stars for each halo mass bin. Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side. Lines of constant star formation efficiency are overplotted. We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$. The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$.

@@

>>>>

Once a halo becomes chemically enriched by the death of its Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10, Smith15}. Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars. These stars still are metal-poor, having metallicities of 10$^{-6}$ - 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2000 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and uses the cosmological parameters from the Planck collaboration best fit 
\citet{Planck13_Cosmo}: $\Omega_{M}$ = 0.3175, $\Omega_{\Lambda}$ = 
0.6825, $\Omega_{DM}$ = 0.2685, and h = 0.6711, with the variables 
having their usual definitions. The simulation is run until $z$ = 9.32, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.

@@

If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from W12 \citep{Hirano17}. This results in an exponential cutoff before M$_{\rm char}$ and a power-law IMF after. Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}. We are only tracking massive Pop III star formation.

@@

%====================================================================
\subsubsection{Pop II  Star Formation and Feedback}
%====================================================================
The Pop II star formation model is the same as \citet{Wise09}, which is equivalent to the above criteria for Pop III star formation but without the molecular hydrogen fraction requirement, and with a metallicity greater than the above value. Star formation is only allowed for gas with temperatures $T$ < 1000 K, to ensure that the volume is cold and collapsing. Contrary to Pop III stars representing single star particles, metal-enriched star particles are modelled as clusters of stars. We enforce a minimum mass of M$_{\rm min}$ = 1000 M$_{\odot}$ for these star particles.

@@

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor can affect the column density of \hh{}, we can examine $N_{\rm H2}$ to the core as a function of halo mass for an isothermal halo, with a constant \hh{} fraction. The total number of \hh{} molecules within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$ is the critical density. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$ with $f_{c} = 10^{-2}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}
For $z = 15$ and $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, Figure \ref{fig:H2_column_mass} shows the \hh{} column density as a function of halo mass. Here, the shielding factor is simply $f = 10^{\rm x} / f_{\rm H2}$, and is multiplied to the column density, effectively adjusting the \hh{} fraction within the halo. As the shielding factor increases, the column density can effectively increase by an order of magnitude. The effect of the shielding factor on the column density of \hh{} within a halo is critical in understanding how LW feedback might affect these halos. (More needs to be said here. I'd like to make it more clear about why the shielding factor changes, one way or the other, and the effects of that change. I don't think the plot shows exactly what we want.)

@@

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
    \caption{The star formation rate density of Pop III stars. The SFRD peaks at a redshift of 20, and slowly falls off. Note that metal-enriched star formation continually increases throughout time, although that is not plotted here. Due to the small box size of our simulation, this SFRD is particular for our box, and would change for larger, or smaller box sizes.}
    \label{fig:pop3_SFR_bar}
\end{figure}

In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}. The median for each bin is represented by an x, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively. The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq. \ref{LWbg} is shown as the black solid line. Notably, the mean halo mass falls well below the relation, at 10$^{5.9}$ M$_{\odot}$ until $z$ = 11.5, at which point, the mean halo mass rises to 10$^{6.6}$ M$_{\odot}$. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times. In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts. Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}. As can be seen by the red solid line in \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation. The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times. This galaxy has a halo mass of $10^{8.5} M_{\odot}$, a total stellar mass of $10^{6.5} M_{\odot}$, and has a peak Pop III SFR of $10^{-3.5} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $10^{-1.3}$ at $\approx$ 500 Myr. This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars. This increase in the LW background can also be seen in Figure \ref{fig:JLW_xe_mass}, where by the end of the simulation, the LW background rises to greater than 1 $J_{21}$.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus redshift. The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass. The error bars indicate the 15.9 and 84.1 percentiles. The right hand side shows the percentage of halos that fall below the M01 mass threshold as a function of redshift. The M01 mass threshold (Eq. \ref{mthresh}), is plotted for the constant LW background in Eq. \ref{LWbg}. Almost all halos fall below the M01 relation, until $z$ = 11.5, when the mean halo mass rises above the relation.}
    \label{fig:mean_mass}
\end{figure}

@@

The LW background intensity versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}. Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq. \ref{mthresh}) for the given LW background (Eq. \ref{LWbg}) is the solid black line. We see again that almost all halos form Pop III stars below the M01 threshold. There are also a few halos that form Pop III stars in very high J$_{\rm LW}$, below the relation. This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 100 pc of each other. Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation. The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs synchronically, star formation will not be suppressed, so long as they are a suitable distance away from each other. As there are only a few data points in this region, this situation is rare. It should be noted that there are duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation. The grouped points in the higher end of J$_{\rm LW}$ are representative of such halos. We find that a total of 84\% of the halos forming Pop III stars lie below the M01 mass threshold over the entire simulation redshift range. We also do not see a clear relationship between the LW intensity and the host halo mass. This may be showing that the LW intensity is not as great an indicator of which halo will be allowed to form a Pop III star as previously thought.

@@

We now inspect the number of Pop III stars and the total mass of Pop III stars per halo. Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses < $1 M_{\odot}$. Figure \ref{fig:totnump3_halomass_sidehist} shows the number of Pop III stars per halo for a given halo mass, just after star formation. The histogram of the number of Pop III stars for all masses is projected on the right hand side. We find that a median number of four Pop III stars form per halo, with a maximum of 16 Pop III stars forming per halo. Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo. Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars. It should be noted that these halos aren't necessarily forming all of the Pop III stars at once. For example, a halo can form stars again if it din't host a supernova. The number of Pop III stars that form within a halo is indicative of the star formation history of that halo. Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side. Lines of constant star formation efficiency are overplotted. We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$. The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$.

At the end of the simulation, Figure \ref{fig:final_redshift_Np3_mass} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star. The red line shows the median number of Pop III stars for each halo mass bin. At low masses, the number of Pop III stars per halo sits around 2 Pop III stars, and quickly rises once the halo mass reaches $10^{7} M_{\odot}$. We can also look at the spread in creation times of these Pop III stars per halo, shown in Figure \ref{fig:p3spread_mass}. The halos that have a zero spread in their Pop III creation time, meaning the Pop III stars formed at the same time, lie at $10^{-3}$ Myr. The red line indicates the median spread in creation times for each halo mass bin. There are two groups within this plot. The first group contains halos that form their Pop III stars in a spread of < 10 Myr, with a median spread of about $10^{-1}$ Myr. The second group contains halos that form their Pop III stars in a spread of > 10 Myr, with a median spread of about 100 Myr. The second group represents typically larger mass halos that have acquired older Pop III stars by the end of the simulation through their long merger history. These halos have acquired these Pop III stars from outside halos, accounting for the large spread in Pop III creation time as well as the increased number of Pop III stars, as seen in Figure \ref{fig:final_redshift_Np3_mass}.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/p3spread_mass.pdf}
    \caption{The spread in Pop III creation times per halo versus halo mass at the end of the simulation. The red line indicates the median spread in creation times for each halo mass bin. There are two groups that appear in this plot, halos that have a spread of less than 10 Myr, representing halos that form Pop III stars quickly, and halos that have a spread of greater than 10 Myr, representing larger mass halos that acquire old Pop III stars through mergers.}
    \label{fig:p3spread_mass}
\end{figure}
